Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-30 paper/paper.tex
paper: Add Contribution

Finally, we have compared the results obtained with the model we purposed with another
method that involves tools from the Virtual Observatory such as Clusterix \cite{balaguer2020clusterix}.

@@

Since the components of the open cluster are born from the same gas cloud and they
share both dynamic properties and relative distance, as well as age and chemical
composition, the first step is to analyze the proper motion configuration space of
the region of interest. This approach is the one used by many tools from the Virtual
Observatory such as TOPCAT \cite{taylor2005topcat}, Clusterix 2.0 \cite{balaguer2020clusterix},
Aladin \cite{bonnarel2000aladin} or VOSA \cite{bayo2008vosa}.

@@

>>>>

Finally, we have compared the results obtained with the model we purposed with another
method that involves tools from the Virtual Observatory (VO) such as Clusterix \cite{balaguer2020clusterix}.

@@

Since the components of the open cluster are born from the same gas cloud and they
share both dynamic properties and relative distance, as well as age and chemical
composition, the first step is to analyze the proper motion configuration space of
the region of interest. This approach is the one used by many tools from the VO
such as TOPCAT \cite{taylor2005topcat}, Clusterix 2.0 \cite{balaguer2020clusterix},
Aladin \cite{bonnarel2000aladin} or VOSA \cite{bayo2008vosa}.

@@

The developed method is successful since it meets all our established requirements:

\begin{itemize}
  \item Our method gives valid results compatible with current methods as described in Section \ref{sec:results}.
  \item As required from the beginning, it is non-supervised and non-parameterized.
  \item The model shows a great performance compared with current methods.
  \item It is able to deal with large and dense regions. As an example,
        it has succeeded characterizing Melotte 25 (Hiades) OC. This cluster is
        really large and dense, and its relative proximity makes it difficult to
        characterize. Clusterix fails characterizing this cluster. In this case,
        our method proposes at least two more non-catalogued clusters. The analysis
        of these new clusters brings out an interesting stellar dynamics in the studied
        region. It could mean that there was a recent interaction among different molecular clouds.
\end{itemize}

For all this, we consider that the presented method is good enough to be included
in the Virtual Observatory toolset. Only a few tweaks must be done in order to make
our model compatible with other tools of the VO.
